OneD: increasing reproducibility of Hi-C Samples with abnormal karyotypes

### 2017-06-01 main.tex
Wrote the abstract.

\title[Dryhic]{Dryhic: Increasing Reproducibility of Hi-C Samples with Abnormal Karyotypes}

\author[Vidal \textit{et~al}.]{Enrique Vidal\,$^{\text{\sfb 1,2}*}$, François le Dily\,$^{\text{\sfb 1,2}}$, Javier Quilez\,$^{\text{\sfb 1,2}}$, Ralph Stadhouders\,$^{\text{\sfb 1,2}}$, Yasmina Cuartero\,$^{\text{\sfb 1,2}}$ Guillaume Fillion\,$^{\text{\sfb 1,2}}$ and Miguel Beato\,$^{\text{\sfb 1,2}}$}

@@

\abstract{
	\textbf{Motivation:} Several strategies have been proposed to remove biases from Hi-C experiments. However, samples with abnormal karyotypes (such as cancer cell lines) present challenges not completely addressed by existing methods. We introduce an alternative designed to model the total number of contacts per genomic loci, thus taking into account possible chromosomal abnormalities.\\
	\textbf{Results:} The proposed method increases reproducibility among replicas of Hi-C samples with abnormal karyotype and obtained using different protocols. The implementation is fast and scales well in terms of computing resources for resolutions up to 1 Kbp.\\	
	\textbf{Availability:} The strategy proposed is implemented as an R package available at \href{http://www.github.com/qenvio/dryhic}{http://www.github.com/qenvio/dryhic}.\\	
	\textbf{Contact:} \href{enrique.vidal@crg.eu}{enrique.vidal@crg.eu}\\	
	\textbf{Supplementary information:} Supplementary data are available at \textit{Bioinformatics}	online.}
\maketitle

@@

This work has been supported by the... Text Text  Text Text.\vspace*{-12pt}

>>>>

\title[Dryhic]{OneD: increasing reproducibility of Hi-C Samples with abnormal karyotypes}

\author[Vidal \textit{et~al}.]{Enrique Vidal\,$^{\text{\sfb 1,2}*}$, François le Dily\,$^{\text{\sfb 1,2}}$, Javier Quilez\,$^{\text{\sfb 1,2}}$, Ralph Stadhouders\,$^{\text{\sfb 1,2}}$, Yasmina Cuartero\,$^{\text{\sfb 1,2}}$,Miguel Beato\,$^{\text{\sfb 1,2}}$ and Guillaume Fillion\,$^{\text{\sfb 1,2}}$}

@@

\abstract{
  \textbf{Motivation:} The three-dimensional conformation of genomes is an
essential component of their biological activity. The advent of the Hi-C
technology enabled an unprecedented advance in our understanding of genome
structures. However, Hi-C is subject to systematic biases that can
compromise downstream analyses. Several strategies have been proposed to
remove those biases, but none of them addresses the common issue of
abnormal karyotypes. Many experiments are performed in cancer cell lines,
which typically harbor large-scale copy number variations that create
visible defects on the raw Hi-C maps. The consequences of these widespread
artifacts on the normalized maps have not been investigated so far.\\
	\textbf{Results:}
We observed that current normalization methods perform badly in the
presence of large-scale copy number variations, obscuring biological
viarations and enhancing batch effects. To address this issue, we
developed an alternative appoach designed to take into account chromosomal
abnormalities. The method, called OneD, increases reproducibility among
replicates of Hi-C samples with abnormal karyotype, thus significantly
outperforming previous methods.  In the absence of chromosomal
aberrantions, OneD fared equally well as state-of-the-art methods, making
it a safe choice for Hi-C normalization. OneD is fast and scales well in
terms of computing resources for resolutions up to 1 kbp.\\	
	\textbf{Availability:} OneD is implemented as an R package available at \href{http://www.github.com/qenvio/dryhic}{http://www.github.com/qenvio/dryhic}.\\	
	\textbf{Contact:} \href{enrique.vidal@crg.eu}{enrique.vidal@crg.eu}\\	
	\textbf{Supplementary information:} Supplementary data are available at \textit{Bioinformatics}	online.}
\maketitle

@@

This work was supported by the Spanish Ministry of Economy and
Competitiveness, ‘Centro de Excelencia Severo Ochoa 2013-2017’,
SEV-2012-0208, ERC Synergy Grant 609989 (GF) and...
\vspace*{-12pt}
